### 2019-03-25 paper/sex_selection_spacing-ver2-demography.tex
Cannot have identifiable information on submission

\title{Birth Spacing in the Presence of Son Preference and Sex-Selective Abortions:
India's Experience over Four Decades%
\protect\thanks{%
I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
I owe thanks to Shelly Lundberg, Daniel Rees, David Ribar, 
Hendrik Wolff, seminar participants at University of Copenhagen, University of Michigan, 
University of Washington, University of Aarhus, the Fourth 
Annual Conference on Population, Reproductive Health, 
and Economic Development, and the Economic Demography Workshop for helpful 
suggestions and comments.
I would also like to thank Nalina Varanasi for research assistance.
Support for development of the method from the University of Washington Royalty 
Research Fund and the Development Research Group of the World Bank is gratefully 
acknowledged.
The views and findings expressed here are those of the author and
should not be attributed to the World Bank or any of its member countries.
Partial support for this research came from a Eunice Kennedy Shriver National
Institute of Child Health and Human Development research infrastructure grant,
5R24HD042828, to the Center for Studies in Demography and Ecology at the
University of Washington.
}
}

\author{Claus C P\"ortner\\
    Department of Economics\\
    Albers School of Business and Economics\\
    Seattle University, P.O. Box 222000\\
    Seattle, WA 98122\\
    \href{mailto:claus@clausportner.com}{\texttt{claus@clausportner.com}}\\
    \href{http://www.clausportner.com}{\texttt{www.clausportner.com}}\\
    \& \\
    Center for Studies in Demography and Ecology \\
    University of Washington\\ \vspace{2cm}
    }

@@

\setcounter{page}{-1}
\maketitle
\thispagestyle{empty}

% \setcounter{page}{0}

\newpage
\thispagestyle{empty}
\doublespacing

>>>>

\title{Birth Spacing in the Presence of Son Preference and Sex-Selective Abortions:
India's Experience over Four Decades%
% \protect\thanks{%
% I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
% I owe thanks to Shelly Lundberg, Daniel Rees, David Ribar, 
% Hendrik Wolff, seminar participants at University of Copenhagen, University of Michigan, 
% University of Washington, University of Aarhus, the Fourth 
% Annual Conference on Population, Reproductive Health, 
% and Economic Development, and the Economic Demography Workshop for helpful 
% suggestions and comments.
% I would also like to thank Nalina Varanasi for research assistance.
% Support for development of the method from the University of Washington Royalty 
% Research Fund and the Development Research Group of the World Bank is gratefully 
% acknowledged.
% The views and findings expressed here are those of the author and
% should not be attributed to the World Bank or any of its member countries.
% Partial support for this research came from a Eunice Kennedy Shriver National
% Institute of Child Health and Human Development research infrastructure grant,
% 5R24HD042828, to the Center for Studies in Demography and Ecology at the
% University of Washington.
% }
}

\author{}
% \author{Claus C P\"ortner\\
%     Department of Economics\\
%     Albers School of Business and Economics\\
%     Seattle University, P.O. Box 222000\\
%     Seattle, WA 98122\\
%     \href{mailto:claus@clausportner.com}{\texttt{claus@clausportner.com}}\\
%     \href{http://www.clausportner.com}{\texttt{www.clausportner.com}}\\
%     \& \\
%     Center for Studies in Demography and Ecology \\
%     University of Washington\\ \vspace{2cm}
%     }

@@

% \setcounter{page}{-1}
\maketitle
\thispagestyle{empty}

\setcounter{page}{0}

% \newpage
\thispagestyle{empty}
\doublespacing
